RNA-seq from 4 cell populations

### 2021-08-04 deconvolution/fans4/molec_profiling.Rmd
bug fix

```{r load.packages, echo=FALSE, message=FALSE, results='hide', cache=FALSE}
suppressPackageStartupMessages({
library(variancePartition)
library(limma)
library(edgeR)
library(mvIC)
library(reshape2)
library(qvalue)
library(data.table)
library(BiocParallel)
library(knitr)
library(org.Hs.eg.db)
library(kableExtra)
library(ggplot2)
library(cowplot)
library(scran)
library(SummarizedExperiment)
library(gridExtra)
library(openxlsx)
library(synapser)
library(zenith)
library(nnet)
library(PRROC)
library(githubr)
synLogin()
library(EnsDb.Hsapiens.v86)
detach("package:EnsDb.Hsapiens.v86", unload=TRUE)
library(EnsDb.Hsapiens.v86)
})

@@

>>>>

```{r load.packages, echo=FALSE, message=FALSE, results='hide', cache=FALSE}
suppressPackageStartupMessages({
library(variancePartition)
library(limma)
library(edgeR)
library(mvIC)
library(reshape2)
library(qvalue)
library(data.table)
library(BiocParallel)
library(knitr)
library(org.Hs.eg.db)
library(kableExtra)
library(ggplot2)
library(cowplot)
library(scran)
library(SummarizedExperiment)
library(gridExtra)
library(openxlsx)
library(synapser)
library(zenith)
library(UpSetR)
library(nnet)
library(PRROC)
library(githubr)
synLogin()
library(EnsDb.Hsapiens.v86)
detach("package:EnsDb.Hsapiens.v86", unload=TRUE)
library(EnsDb.Hsapiens.v86)
})

@@

```{r disease.upsetr}
de_genes = lapply(levels(info$CellType), function(CT){

  tabl = topTable( fitDisease, coef = key, number=Inf)
  tabl$ensID = rownames(tabl)
  rownames(tabl[tabl$adj.P.Val < 0.05,])
  })
names(de_genes) = levels(info$CellType)

lst = fromList(de_genes)
a = upset(lst, keep.order = FALSE, order.by="freq" )

upset(lst, keep.order = FALSE, order.by="freq", sets.bar.color=colorCodes[a$Set_names] )
```
